Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-09-13 writeup/conStruct.tex
added fastStr time comparison

For values of $K<4$, the spatial model was strongly preferred over the nonspatial model (Fig \ref{populus_xvals}),
the results of which were broadly concordant with those of the fastSTRUCTURE runs (Fig \ref{populus_fastStr}).
Most of this signal seems to derive from the \textit{P. trichocarpa} samples:
covariance within predominantly \tri{} layers decays more quickly with distance
than within the majority \bals{} layer, as seen in Fig \ref{populus_sp_layer_covs}.  
This indicates that, although isolation by distance is a feature of the dataset as a whole, 
its magnitude varies considerably across biological units - 
an aspect of the data \texttt{conStruct} is able capture well.
Based on our cross-validation results we view the $K=3$ spatial model 
as a sufficient description of the data.

@@

For a relatively small number of samples, 
\texttt{conStruct} can be much faster than other nonspatial clustering methods.
On a desktop machine with a 4.2 GHz Intel Core i7 processor, 
an analysis of the black bear dataset (84 samples, 21,000 loci) 
running \texttt{conStruct}'s spatial model with 4 layers for 5,000 MCMC iterations, 
which was more than sufficient for convergence,
took XXX hours.
On the same machine and dataset, 
a fastSTRUCTURE run with $K=4$ took 3.76 days.
However, for a large number of samples, 
fastSTRUCTURE (or ADMIXTURE) would be much faster.

>>>>

For values of $K<4$, the spatial model was strongly preferred over the nonspatial model (Fig \ref{populus_xvals}),
the results of which were broadly concordant with those of the fastSTRUCTURE runs (Fig \ref{populus_fastStr}).
\gb{come back to this}.
Most of this signal seems to derive from the \textit{P. trichocarpa} samples:
covariance within predominantly \tri{} layers decays more quickly with distance
than within the majority \bals{} layer, as seen in Fig \ref{populus_sp_layer_covs}.  
This indicates that, although isolation by distance is a feature of the dataset as a whole, 
its magnitude varies considerably across biological units - 
an aspect of the data \texttt{conStruct} is able capture well.
Based on our cross-validation results we view the $K=3$ spatial model 
as a sufficient description of the data.

@@

For a relatively small number of samples, 
\texttt{conStruct} can be much faster than other nonspatial clustering methods.
On a desktop machine with a 4.2 GHz Intel Core i7 processor, 
an analysis of the black bear dataset (84 samples, 21,000 loci) 
running \texttt{conStruct}'s spatial model with 4 layers for 5,000 MCMC iterations, 
which was more than sufficient for convergence,
took 2.8 hours.
On the same machine and dataset, 
a fastSTRUCTURE run with $K=4$ took 90.2 hours.
However, for a large number of samples, 
fastSTRUCTURE (or ADMIXTURE) would be much faster.
